\begin{abstract}
We present a source-grounded pipeline for evaluating legal reasoning in large
language model outputs. The pipeline begins with a legal source case rather than
a hand-authored benchmark question. An LLM agent, Frank, extracts the legal
issue, controlling doctrine, source-grounded gold answer, and controlled
boundary variations. Karthic generates a fresh rubric from the locked Frank
packet. A roster of LLMs then answers the same generated question using the
natural question-only protocol. Dasha extracts normalized legal-reasoning
signatures from those answers and clusters them into interpretable centroids. A
rubric-guided LLM judge scores each centroid, projects centroid scores to all
responses in the cluster, and produces model rankings. Zak creates escalation
packets only when uncertainty, disagreement, or mixed clusters require further
review.

We report internal validation on a Statute-of-Frauds calibration case drawn from
a real court-case PDF. The evidence combines stage-level artifact assessment, a
60-response live perturbation-aware model batch over ten model identifiers, and
a deterministic 500-response regression suite over eight Statute-of-Frauds
reasoning archetypes. The live batch answered three Frank-generated tracks:
the original question, an invariant party-name edit, and a material signed-
writing edit. Dasha clustered all 60 unlabeled natural answers into 22
track-aware legal-reasoning centroids with complete member coverage. The
invariant edit preserved the dominant answer family, while the material edit
shifted the dominant answer family. A two-model judge panel produced 220
final row-level scores; an adjudicator resolved unstable panel rows before score
projection and model ranking. The controlled stress suite produced eight
expected clusters with cluster purity, completeness, and macro-F1 equal to 1.0.
These results support internal technical review of the pipeline as a
reproducible research method:
Frank produces a source-grounded benchmark packet, Karthic produces a dynamic
rubric, Dasha separates observed legal-reasoning paths, Judge applies the rubric
row by row, and Zak records escalation state. They do not yet establish external
legal validity across legal domains: held-out cases and expert legal review
remain required before stronger academic claims.
\end{abstract}
