\section{Artifact Examples}

This appendix shows concrete artifacts from the live internal-validation run. The examples are generated from the run bundle rather than rewritten by hand.

\subsection{Frank Packet Example}

The following fields are direct excerpts from the live Frank packet. They show the source-derived scenario, expected answer, and the perturbation tracks that later generated model responses.

\begin{longtable}{p{0.18\linewidth}p{0.72\linewidth}}
\toprule
Frank field & Live output excerpt \\
\midrule
Source & cases/MarriageSoF\_Anglemire v Policemens Benev Assn of Chicago.pdf \\
Doctrine family & Statute of Frauds - agreements made upon consideration of marriage (oral promise to confer property/beneficiary status in exchange for marriage) \\
Neutral question & In Illinois, Clinton has long been a member of a fraternal benefit association that pays a death benefit to the member's named beneficiary. Under the association's constitution and bylaws, a member may change beneficiaries. The bylaws also provide that if the member cannot surrender the existing certificate for cancellation, he may instead file an affidavit explaining why he cannot produce it and naming a new beneficiary; upon that affidavit, the association will cancel the old certificate and issue a new one that is binding on the member, the beneficiaries, and the association. Before marrying Amanda, Clinton orally tells her: "If you marry me, I will surrender my current certificate and obtain a new certificate naming you as beneficiary." Amanda marries Clinton relying on that promise. After the marriage, Clinton has the association issue a new certificate naming Amanda as beneficiary, and Amanda keeps that certificate. About a year later, after serious marital conflict, Clinton asks the association to change beneficiaries again. He tells the association he cannot produce the certificate because Amanda has it, signs the associa... \\
Gold answer & Bottom-line outcome: No. The premarital oral promise made in consideration of marriage is void/unenforceable under the Statute of Frauds, and the subsequent marriage (and even the later voluntary act of initially naming Amanda as beneficiary) does not remove the promise from the statute. Therefore Clinton could later change beneficiaries in compliance with the association bylaws, and the later-named beneficiaries take. Controlling doctrine: Statute of Frauds provision requiring a writing for agreements made upon consideration of marriage (other than the mutual promise to marry). Writing requirement and trigger: Illinois requires that an agreement made upon consideration of marriage be in writing and signed by the party to be charged. The trigger is satisfied here because Clinton's promise was explicitly conditioned on Amanda marrying him (consideration of marriage) and concerned settl... \\
Variation V\_surface\_invariant (invariant) & Changed fact: Only party and organization names are changed; all legally operative facts, dates, writings, performances, and later disputes remain the same. Expected behavior: answer\_invariant; the dominant legal reasoning and outcome should not change. Question: In Illinois, Jordan has long been a member of a fraternal benefit association that pays a death benefit to the member's named beneficiary. Under the association's constitution and bylaws, a member may change beneficiaries. The bylaws also provide that if the member cannot surrender the existing certificate for cancellation, he may instead file an affidavit explaining why he cannot produce it and naming a new beneficiary; upon that affidavit, the association will cancel the old certificate and issue a new one that is binding on the member, the beneficiaries, and the association. Before marrying Alex, Jordan orally tells her: "... \\
Variation V1 (material) & Changed fact: Before the wedding, Clinton signs a short written note stating: "In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate," and signs it. Expected behavior: Model should recognize that the marriage-consideration agreement is no longer barred for lack of writing (likely satisfying the SOF), but must still analyze whether that enforceable agreement actually restricts Clinton's contractual/bylaw power to change beneficiaries (and what remedy follows). The outcome is not fully resolved by the source; answer should be conditional and flag that the source chiefly addresses the no-writing scenario. Question: In Illinois, Clinton is a member of a fraternal benefit association whose bylaws allow him to change beneficiaries and also allow a change by affidavit if he cannot surrender the existing certificate. Before marrying Amanda, Clin... \\
Variation V2 (material) & Changed fact: Clinton's promise is not conditioned on marriage; he promises after engagement: "Regardless of whether we marry, I'll name you beneficiary," and Amanda later marries for independent reasons. Expected behavior: Question: In Illinois, Clinton has long held a death-benefit certificate in a fraternal benefit association whose bylaws allow him to change beneficiaries (including by affidavit if he cannot surrender the existing certificate). While engaged to Amanda, Clinton orally tells her: "Even if we never marry, I'm going to name you as beneficiary on my association certificate." Amanda does not promise anything in return, and her later decision to marry Clinton is for independent personal reasons, not as consideration for the beneficiary promise. After the marriage, Clinton has the association issue a new certificate naming Amanda as beneficiary, and she keeps the certific... \\
\bottomrule
\end{longtable}

\subsection{Karthic Rubric Example}

Karthic generated the following row-level scoring instrument from the locked Frank packet. Each row is later applied by Judge to Dasha cluster representatives.

\begin{longtable}{p{0.07\linewidth}p{0.12\linewidth}p{0.08\linewidth}p{0.43\linewidth}p{0.20\linewidth}}
\toprule
Row & Category & Weight & Criterion & Source support excerpt \\
\midrule
R0 & doctrine & 0.16 & Correctly identifies the controlling doctrine as the Illinois Statute of Frauds provision for agreements made upon consideration of marriage (beyond mutual promises to marry) and frames the dispute as enforcement of a premarital bargain exchanging marriage for a property/benefit interest (beneficiary status / restriction on later change). & Frank gates G1; source\_evidence: statute language quoted in packet ("no action… on any agreement made in consideration of marriage, unless… in writing and signed"; "other than the mutual promise to marry"); source\_ext... \\
R1 & rule & 0.14 & States the governing rule: a marriage-consideration agreement is unenforceable unless there is a writing/signed memorandum by the party to be charged (or authorized agent). & Gate G2 rule and source\_evidence; gold\_answer section "Writing requirement and trigger" referencing Ill. Rev. Stat. ch. 59 § 1. \\
R2 & facts & 0.1 & Accurately uses the legally triggering facts: the promise was premarital, explicitly conditioned on marriage ("If you marry me…"), and aimed at obtaining/maintaining beneficiary status on the association certificate; acknowledges there is no signed premarital writing/memorandum. & source\_extraction trigger\_facts (premarital oral promise conditioned on marriage; no written agreement); neutral\_question last paragraph ("Assuming there is no written premarital agreement…"). \\
R3 & rule & 0.14 & Applies the writing requirement to conclude the premarital promise is barred/void/unenforceable as a parol marriage-consideration agreement (i.e., failure of SOF compliance). & Gate G2; gold\_answer bottom line ("premarital oral promise… void/unenforceable under the Statute of Frauds"); source\_evidence that court treated the promise as "parol/oral and therefore void." \\
R4 & exceptions & 0.14 & Correctly rejects part performance/estoppel based on the marriage (and related reliance) as a basis to escape the marriage-consideration Statute of Frauds: marriage after the promise is not part performance for this category and is the precise scenario the statute contemplates. & Gate G3 rule and quoted opinion language in packet ("subsequent marriage… is not… part performance"; "Promise of marriage, followed by the marriage, is the exact situation contemplated by the statute"); gold\_answer "C... \\
R5 & exceptions & 0.1 & Addresses the post-marriage certificate initially naming the spouse and explains (consistent with the source) that it is treated as a voluntary act that does not supply enforceable consideration-based rights that override the Statute of Frauds bar on the premarital bargain. & Gate G4 source\_evidence ("any subsequent act… purely voluntary"); gold\_answer explains initial designation does not remove statute bar. \\
R6 & rule & 0.1 & Separately applies the association constitution/bylaws: if no enforceable contrary obligation exists, the member retains the right to change beneficiaries using the bylaw mechanism (including affidavit when unable to surrender the certificate), making the later-issued certificate effective as to the fund. & Gate G4 rule and source\_evidence ("insured had the right to change the beneficiary… as provided by the constitution and by-laws"; bylaws allowed change by affidavit); source\_extraction trigger\_facts describing affidav... \\
R7 & counterargument & 0.06 & Presents and fairly answers the strongest pro-spouse counterargument: that the arrangement became an "executed contract" after marriage and initial designation, or that equity should estop a later change due to reliance; then explains why the case's reasoning rejects that move for marriage-consideration agreements. & gold\_answer "Strongest counterargument" and rejection rationale tied to G3/G4 (marriage not part performance; post-marriage act voluntary). \\
R8 & conclusion & 0.04 & Gives a clear bottom-line allocation of proceeds consistent with the source-grounded outcome: spouse cannot enforce the premarital promise to defeat the later bylaw-compliant change; later-named beneficiaries take. & gold\_answer bottom line; source\_extraction holding summary (appellate court held promise void; member could change beneficiaries under bylaws). \\
R9 & variation & 0.02 & Shows sensitivity to legally meaningful variations flagged by the packet (e.g., a signed premarital memorandum could satisfy the writing requirement; a promise not conditioned on marriage may not trigger the marriage-consideration SOF gate) and avoids overstating the source beyond the no-writing scenario. & variations V1 (signed note; outcome not fully resolved by source) and V2 (promise not conditioned on marriage); source\_limits noting Illinois-specific and that the case chiefly addresses the no-writing scenario. \\
\bottomrule
\end{longtable}

\subsection{Model Response Examples}

\begin{longtable}{p{0.18\linewidth}p{0.13\linewidth}p{0.61\linewidth}}
\toprule
Model & Dasha cluster & Response excerpt \\
\midrule
gpt-5.2 & original\_\_cluster\_1 & No. \#\#\# 1) The premarital promise is within the Illinois Statute of Frauds and is unenforceable without a writing In Illinois, an oral promise **made in consideration of marriage** ("If you marry me, I will …") falls within the Statute of Frauds (750 ILCS 80/1, traditional "marriage consideration" provision). A promise to confer a property benefit on a spouse in exchange for marrying-such as a promise to keep the spouse as beneficiary of a death benefit-must be in a signed writing to be enforceable. Here, the promise was explicitly conditioned on marriage and there is **no signed premarital agreement or memorandum**, so the underlying contract claim fails. \#\#\# 2) Marriage (and related rel... \\
gpt-5.2 & original\_\_cluster\_2 & No. \#\#\# 1) The premarital promise is within the Statute of Frauds In Illinois, an oral promise made *in consideration of marriage* ("marry me and I will do X") falls within the Statute of Frauds and is unenforceable unless there is a writing signed by the promisor (or an equivalent signed memorandum). A promise to name (or keep) a spouse as beneficiary because she marries him is the classic "marriage consideration" contract. So, absent a signed writing, Amanda cannot sue to enforce Clinton's premarital promise as a contract. \#\#\# 2) Marriage (and related reliance) does not supply part performance to avoid that bar Illinois does not treat the marriage itself as "part performance" that takes... \\
gpt-5.4 & original\_\_cluster\_1 & No. Under Illinois law, Amanda would almost certainly lose, and the later bylaw-compliant change of beneficiary would control. \#\# Why \#\#\# 1. The premarital promise is within the Statute of Frauds A promise made **in consideration of marriage**-for example, "marry me and I'll give you this property/right/benefit"-must generally be **in writing** to be enforceable, unless it is merely a mutual promise to marry. Clinton's statement was not just "I'll marry you." It was a collateral promise: if Amanda married him, he would make her beneficiary of the fraternal benefit certificate. That is the kind of marriage-based promise Illinois treats as falling within the Statute of Frauds. Because there... \\
gpt-5.4 & original\_\_cluster\_1 & No. Under Illinois law, Amanda would almost certainly lose, and the later bylaw-compliant change of beneficiary would control. \#\# Why \#\#\# 1. The premarital promise is within the Statute of Frauds A promise made **in consideration of marriage**-other than the mutual promise to marry itself-must be in writing to be enforceable. Clinton's statement was essentially: - *"If you marry me, I will make you beneficiary."* That is a classic **promise upon consideration of marriage**. Since there is: - no written premarital agreement, and - no signed memorandum, Amanda cannot enforce that promise as a contract. \#\# 2. Marriage itself is not enough part performance Illinois follows the rule that **mar... \\
claude-sonnet-4-6 & original\_\_cluster\_1 & \# Amanda's Claim to the Death Benefit: Legal Analysis \#\# Overview of the Problem This question sits at the intersection of several doctrines: the Statute of Frauds (particularly the marriage provision), promissory estoppel, part performance, the contractual rights of fraternal benefit association members, and the enforceability of beneficiary designations. The short answer is that **Amanda faces serious obstacles and will likely fail**, though the analysis is genuinely complex and some arguments have real force. --- \#\# I. The Threshold Problem: Statute of Frauds \#\#\# A. The Marriage Provision Illinois follows the traditional Statute of Frauds, which requires that promises *made in consider... \\
claude-sonnet-4-6 & original\_\_cluster\_3 & \# Amanda's Claim to the Death Benefit: Legal Analysis \#\# Overview of the Problem This question sits at the intersection of four distinct legal doctrines: (1) the Statute of Frauds as applied to premarital promises, (2) promissory estoppel and part performance, (3) the contractual/quasi-contractual enforceability of beneficiary designations in fraternal benefit certificates, and (4) the internal governance rules of fraternal benefit associations and their legal effect on third-party claims. The short answer is that Amanda faces serious obstacles but has plausible arguments, and the outcome turns substantially on which theory she advances and how Illinois courts weigh competing consideratio... \\
claude-haiku-4-5-20251001 & original\_\_cluster\_7 & \# Analysis of Amanda's Claims to the Death Benefit This is a challenging case involving the intersection of contract law, the Statute of Frauds, promissory estoppel, and the nature of beneficiary designations. Amanda faces significant obstacles, though she has some arguable claims. \#\# I. The Oral Promise and Statute of Frauds \#\#\# The Core Problem Amanda's most direct claim-breach of Clinton's oral promise to name her beneficiary-runs headlong into the **Statute of Frauds**. Under Illinois law (following the Restatement): - **Marriage itself is a consideration** for the promise, so the promise falls within the marriage provision of the Statute of Frauds (contracts made in consideration of... \\
claude-haiku-4-5-20251001 & original\_\_cluster\_6 & \# Analysis of Amanda's Claims This is a nuanced problem involving the intersection of contract law, promissory estoppel, part performance doctrine, and the enforceability of beneficiary designations. Amanda faces substantial obstacles. \#\# I. The Statute of Frauds Problem \#\#\# A. Express Contract Claim Amanda's strongest argument is that Clinton made an enforceable contract: "Marry me and I'll name you beneficiary." However, this faces the **statute of frauds**. **Illinois recognizes a statute of frauds for:** - Contracts in consideration of marriage (Ill. Comp. Stat. 815 ILCS 105/2) - Contracts that cannot be performed within one year **Critical issue:** Is a promise to name someone as a b... \\
google/gemini-3-flash & original\_\_cluster\_2 & Under Illinois law, Amanda likely **cannot** enforce the oral premarital promise to invalidate the later beneficiary change. Her claim would likely fail due to the **Statute of Frauds** and the **Illinois Uniform Premarital Agreement Act (IUPAA)**, and her arguments for equitable relief (part performance or estoppel) are generally unsuccessful in this specific context. Here is the legal breakdown of why Amanda would likely lose: \#\#\# 1. The Writing Requirement (IUPAA and Statute of Frauds) In Illinois, any agreement made in consideration of marriage must be in writing. * **IUPAA (750 ILCS 10/):** Since 1990, Illinois has followed the Uniform Premarital Agreement Act. Section 3 of the Act e... \\
google/gemini-3-flash & original\_\_cluster\_1 & Under Illinois law, Amanda will likely **fail** in her attempt to enforce the oral premarital promise or to invalidate the subsequent beneficiary change. The resolution of this case depends on the intersection of the Illinois Statute of Frauds, the Illinois Uniform Premarital Agreement Act (IUPAA), and the law governing beneficiary designations in fraternal benefit associations. \#\#\# 1. The Statute of Frauds and the IUPAA The primary obstacle for Amanda is the requirement that agreements made in consideration of marriage must be in writing. * **The IUPAA (750 ILCS 10/1 et seq.):** Illinois adopted the Uniform Premarital Agreement Act in 1990. Section 3 of the Act explicitly states: "A prem... \\
google/gemini-3-pro & original\_\_cluster\_2 & Based on Illinois law, **no, Amanda cannot enforce the premarital promise or use estoppel/part performance to invalidate the later beneficiary change.** The death benefit will be awarded to Clinton's children and sister. Here is the legal analysis of why Amanda's claim will fail: \#\#\# 1. The Statute of Frauds Under the Illinois Statute of Frauds (740 ILCS 80/1), any agreement made upon consideration of marriage must be in writing and signed by the party to be charged. Clinton's promise to name Amanda as his beneficiary was made orally and strictly in consideration of her marrying him. Because there is no written premarital agreement or signed memorandum, the contract is unenforceable. \#\#\#... \\
google/gemini-3-pro & original\_\_cluster\_2 & Based on Illinois law, **no, Amanda cannot enforce the premarital promise or use estoppel/part performance to invalidate the later beneficiary change.** The death benefit will be awarded to Clinton's children and sister. Here is the legal analysis of why Amanda's claim will fail: \#\#\# 1. The Statute of Frauds Under the Illinois Statute of Frauds (740 ILCS 80/1), any agreement made in consideration of marriage must be in writing and signed by the party to be charged. Because Clinton's promise ("If you marry me, I will…") was entirely oral, it is presumptively unenforceable. \#\#\# 2. Marriage is Not "Part Performance" Amanda cannot rely on the act of marriage itself to trigger the "part perfor... \\
anthropic/claude-4.5-sonnet & original\_\_cluster\_1 & This is a complex problem involving contract law, the Statute of Frauds, and the interaction between private agreements and organizational bylaws. Let me work through the key issues: \#\# The Statute of Frauds Problem Clinton's premarital promise faces a significant obstacle: **the Statute of Frauds requires contracts made in consideration of marriage to be in writing.** This is one of the classic categories covered by the Statute of Frauds in Illinois and virtually all jurisdictions. Amanda's theories to overcome this: \#\#\# 1. **Part Performance Exception** - Amanda actually married Clinton in reliance on the promise - Clinton initially performed by designating her as beneficiary - Courts a... \\
anthropic/claude-4.5-sonnet & original\_\_cluster\_1 & This is a complex question involving contract law, the statute of frauds, and the rights of fraternal benefit association members. Let me break down the key issues: \#\# The Premarital Promise and Statute of Frauds **Problem for Amanda**: Clinton's oral premarital promise likely falls within the **statute of frauds** as: - A promise made in consideration of marriage (Illinois requires such promises to be in writing) - Under 740 ILCS 80/1, contracts in consideration of marriage must be in writing **Potential exception**: The **part performance doctrine** might apply: - Amanda fully performed by marrying Clinton - Clinton partially performed by initially naming her beneficiary - However, part... \\
openai/gpt-4.1-mini & original\_\_cluster\_1 & This question involves issues of contract enforceability, the statute of frauds, estoppel/part performance, and the effect of the association's bylaws on beneficiary designations. --- \#\#\# Facts summary: - Clinton is a member of a fraternal benefit association that pays death benefits to named beneficiaries. - The bylaws allow members to change beneficiaries by surrendering the certificate or, if unable, by affidavit explaining why the certificate cannot be produced. - Clinton orally promises Amanda before marriage that if she marries him, he will surrender his certificate and get a new one naming her beneficiary. - Amanda marries Clinton relying on this promise. - After marriage, Clinton... \\
openai/gpt-4.1-mini & original\_\_cluster\_1 & Let's analyze the situation step-by-step under Illinois law principles related to contract formation, estoppel, and beneficiary designations in fraternal benefit associations. --- \#\#\# Facts Summary: - Clinton has a certificate naming a beneficiary under a fraternal benefit association. - The association's bylaws allow changing beneficiaries either by surrendering the old certificate or by affidavit if surrender is impossible. - Clinton orally promises Amanda before marriage: if she marries him, he will surrender the old certificate and get a new one naming her beneficiary. - Amanda marries Clinton relying on this promise. - After marriage, Clinton obtains a new certificate naming Amanda b... \\
deepseek-ai/deepseek-r1 & original\_\_cluster\_1 & Based on Illinois law regarding fraternal benefit societies, the Statute of Frauds, and promissory estoppel, **Amanda is unlikely to succeed in enforcing the premarital promise or invalidating the later beneficiary change.** The children/sister should prevail. Here's the analysis: 1. **The Statute of Frauds Bars Enforcement of the Contract:** * Clinton's promise ("If you marry me, I will... name you as beneficiary") constitutes a promise made "in consideration of marriage." Under the Illinois Statute of Frauds (740 ILCS 80/1), such promises **must be in writing and signed by the party to be charged** (Clinton) to be enforceable. * There is no written premarital agreement or signed memoran... \\
deepseek-ai/deepseek-r1 & original\_\_cluster\_1 & Based on Illinois law governing fraternal benefit associations and contract principles, **Amanda likely CANNOT enforce the premarital promise or invalidate the later beneficiary change to recover the proceeds.** Here's the breakdown: 1. **The Premarital Promise as a Contract:** * **Statute of Frauds for Premarital Agreements (750 ILCS 10/1 et seq.):** Illinois law requires premarital agreements to be *in writing* and signed by both parties to be enforceable. Clinton's oral promise ("If you marry me, I will... name you as beneficiary") is precisely the type of promise concerning property rights upon marriage that falls within this statute. * **No Signed Writing:** There is no written prema... \\
meta/meta-llama-3-70b-instruct & original\_\_cluster\_5 & A fascinating question! In this scenario, Amanda is relying on the doctrine of promissory estoppel to enforce Clinton's premarital promise. To succeed, Amanda must demonstrate that: 1. Clinton made a clear and unambiguous promise to name her as the beneficiary. 2. Amanda reasonably relied on that promise by marrying Clinton. 3. Her reliance was detrimental, meaning she gave up something of value (in this case, her freedom to marry someone else or not marry at all). 4. Injustice can be avoided only by enforcing the promise. Here, Amanda has a strong case: * Clinton's oral promise was clear and specific. * Amanda reasonably relied on the promise by marrying Clinton, which is a significant c... \\
meta/meta-llama-3-70b-instruct & original\_\_cluster\_4 & What an interesting case! In Illinois, the court would likely apply the doctrine of promissory estoppel to determine whether Amanda can enforce Clinton's premarital promise. Promissory estoppel is a legal doctrine that allows a party to recover on a promise even if it's not supported by consideration (something of value exchanged) if the following elements are met: 1. A promise was made. 2. The promisor (Clinton) should have reasonably expected the promisee (Amanda) to act in reliance on the promise. 3. The promisee did act in reliance on the promise. 4. Injustice can be avoided only by enforcing the promise. In this case: 1. Clinton made an oral promise to name Amanda as the beneficiary... \\
gpt-5.2 & V\_surface\_invariant\_\_cluster\_3 & No. \#\#\# 1) The premarital promise is within the Statute of Frauds and is not enforceable without a writing In Illinois, a promise **made "in consideration of marriage"** (i.e., "marry me and I'll do X") falls squarely within the Statute of Frauds and is **unenforceable unless there is a written, signed agreement or memorandum**. Jordan's statement-"If you marry me, I will surrender my current certificate and obtain a new certificate naming you as beneficiary"-is exactly that kind of promise. \#\#\# 2) Marriage (and related reliance) does not take this kind of agreement out of the Statute of Frauds in Illinois Alex cannot use **part performance** or **equitable estoppel** based on (a) the mar... \\
gpt-5.2 & V\_surface\_invariant\_\_cluster\_3 & No. \#\#\# 1) The premarital promise is within Illinois's Statute of Frauds and is unenforceable without a writing Illinois requires a signed writing for an **agreement made upon consideration of marriage** (i.e., "marry me and I will do X"), other than mutual promises to marry. Jordan's statement-"If you marry me, I will … obtain a new certificate naming you as beneficiary"-is exactly that kind of bargain. With **no written premarital agreement or signed memorandum**, Alex cannot enforce the promise as a contract to keep her as beneficiary. \#\#\# 2) Marriage (and the later initial designation) does not take this kind of promise out of the Statute of Frauds Illinois does not treat **marriage i... \\
gpt-5.4 & V\_surface\_invariant\_\_cluster\_3 & No. Under Illinois law, Alex is very unlikely to enforce Jordan's premarital oral promise or use estoppel/part performance to defeat the later beneficiary change that complied with the association's bylaws. \#\# Why \#\#\# 1. The oral premarital promise is within the Statute of Frauds A promise made **in consideration of marriage**-"if you marry me, I will do X"-must generally be in writing to be enforceable. Jordan's promise was exactly that: *marry me and I'll name you beneficiary.* Because there is **no written premarital agreement or signed memorandum**, Alex cannot enforce that promise as a contract. \#\#\# 2. Marriage itself is not enough part performance Illinois follows the rule that **ma... \\
gpt-5.4 & V\_surface\_invariant\_\_cluster\_3 & No. Under Illinois law, Alex likely cannot enforce Jordan's premarital oral promise, and the later beneficiary change made in compliance with the association's bylaws will control. \#\# Why \#\#\# 1. The oral promise is within the Statute of Frauds A promise made **in consideration of marriage**-for example, "if you marry me, I will give you property / make you beneficiary"-must be in writing to be enforceable. Jordan's statement was exactly that type of promise: **"If you marry me, I will … obtain a new certificate naming you as beneficiary."** Because there is **no written premarital agreement or signed memorandum**, Alex cannot enforce that promise as a contract. \#\# 2. Marriage itself is no... \\
claude-sonnet-4-6 & V\_surface\_invariant\_\_cluster\_2 & \# Analysis: Alex's Claim Against the Death Benefit Proceeds \#\# Overview of the Legal Problem This question sits at the intersection of several distinct legal doctrines: the Statute of Frauds (particularly the marriage provision), equitable estoppel and part performance, the internal governance rules of fraternal benefit associations, and the competing equities between a surviving spouse and named beneficiaries. The answer is **probably no**-Alex almost certainly cannot prevail-though the analysis is genuinely complex and some equitable arguments deserve serious treatment before being rejected. --- \#\# I. The Threshold Problem: The Statute of Frauds \#\#\# A. The Marriage Provision Illinois fo... \\
claude-sonnet-4-6 & V\_surface\_invariant\_\_cluster\_2 & \# Alex's Claim Against the Death Benefit Proceeds \#\# Executive Summary Alex faces a genuinely difficult case with significant doctrinal obstacles, but has meaningful arguments worth carefully analyzing. The honest assessment is that **Alex likely loses** under orthodox Illinois law, but the claim is not frivolous and a sympathetic court could rule otherwise under equitable theories. Here is the full analysis. --- \#\# I. The Threshold Problem: The Statute of Frauds \#\#\# A. The Promise Falls Within the Marriage Provision Jordan's promise - "marry me and I'll name you beneficiary" - is a promise made **in consideration of marriage**. Under the Illinois Statute of Frauds (740 ILCS 80/1), agreem... \\
claude-haiku-4-5-20251001 & V\_surface\_invariant\_\_cluster\_2 & \# Analysis of Alex's Claim to the Death Benefit This is a challenging case involving the intersection of contract law, the Statute of Frauds, equitable estoppel, and the nature of beneficiary designations. Alex faces significant obstacles but has some arguable claims. \#\# I. The Oral Contract for a Beneficiary Designation \#\#\# A. Statute of Frauds Problem The threshold issue is whether the oral promise is barred by the Statute of Frauds. Illinois courts would likely analyze this under **two potential provisions**: 1. **Marriage provision (Ill. Comp. Stat. 815 ILCS 105/3)**: Promises "in consideration of marriage" must be in writing. Jordan's promise-"If you marry me, I will name you as bene... \\
claude-haiku-4-5-20251001 & V\_surface\_invariant\_\_cluster\_2 & \# Analysis of Alex's Claim to the Death Benefit This is a genuinely difficult question that turns on several intersecting doctrines. The answer is likely **no, Alex cannot recover**, but with meaningful caveats about estoppel theory. \#\# I. The Core Problem: Statute of Frauds \#\#\# A. The Oral Promise and SOF Illinois recognizes that promises made in consideration of marriage are subject to the statute of frauds (Ill. Comp. Stat. 815 ILCS 105/2). The promise-"marry me and I'll name you beneficiary"-is classically within SOF because it's: - Made in consideration of marriage (the marriage itself is the consideration) - Not capable of full performance within one year (the designation is perpetu... \\
google/gemini-3-flash & V\_surface\_invariant\_\_cluster\_3 & Under Illinois law, Alex will likely **not** be able to enforce the oral premarital promise to invalidate the later beneficiary change. The primary obstacles for Alex are the **Statute of Frauds**, the **Illinois Uniform Premarital Agreement Act (IUPAA)**, and the specific way Illinois courts treat marriage as "consideration." Here is the legal breakdown of why Alex's claim would likely fail: \#\#\# 1. The Statute of Frauds and the IUPAA In Illinois, any agreement made in consideration of marriage must be in writing to be enforceable. * **The Statute of Frauds (740 ILCS 80/1):** This long-standing rule requires that any promise made "upon consideration of marriage" must be in writing and sig... \\
google/gemini-3-flash & V\_surface\_invariant\_\_cluster\_3 & Under Illinois law, Alex will likely **not** be able to enforce the oral premarital promise or invalidate the later beneficiary change. The resolution of this issue depends on the intersection of the Statute of Frauds, the Illinois Uniform Premarital Agreement Act (IUPAA), and the law governing fraternal benefit associations. \#\#\# 1. The Statute of Frauds and the IUPAA In Illinois, agreements made in consideration of marriage are subject to strict writing requirements: * **The Illinois Frauds Act (740 ILCS 80/1):** This statute provides that no action shall be brought to charge any person upon any agreement made upon consideration of marriage, unless the agreement is in writing and signed... \\
google/gemini-3-pro & V\_surface\_invariant\_\_cluster\_6 & Based on Illinois law, **Yes, Alex can recover the proceeds.** Although the initial oral promise was subject to the Statute of Frauds, Jordan's subsequent act of actually naming Alex as the beneficiary and delivering the certificate to her constituted **full execution** of the contract. This removed the agreement from the Statute of Frauds and gave Alex a **vested equitable interest** in the death benefit that Jordan could not unilaterally defeat. Here is the step-by-step legal analysis of how Illinois courts resolve this exact scenario: \#\#\# 1. The Statute of Frauds and "Part Performance" Under the Illinois Statute of Frauds (740 ILCS 80/1), any agreement made in consideration of marriage... \\
google/gemini-3-pro & V\_surface\_invariant\_\_cluster\_2 & Based on Illinois law, **Alex cannot enforce the premarital promise or use estoppel/part performance to invalidate the later beneficiary change.** The death benefit will legally go to Jordan's children and sister. Here is the step-by-step legal analysis of why Alex's claims will fail: \#\#\# 1. The Nature of the Beneficiary's Interest Under Illinois law governing fraternal benefit associations and life insurance, a named beneficiary generally has a "mere expectancy" rather than a vested right to the proceeds. The member retains the absolute right to change the beneficiary at any time, provided they comply with the association's constitution and bylaws. The only exception to this rule is if t... \\
anthropic/claude-4.5-sonnet & V\_surface\_invariant\_\_cluster\_1 & This is an excellent multi-layered question involving contract law, the statute of frauds, and the intersection of promissory estoppel with association governance rules. \#\# Alex's Likely Outcome: **Cannot Recover** Despite some equitable arguments, Alex will likely lose because: \#\#\# 1. **The Premarital Promise Issue is Moot** Alex doesn't need to rely on the oral premarital promise because **Jordan actually performed it**-he did change the beneficiary designation to Alex after marriage. The promise was fulfilled, so statute of frauds issues (which would apply to premarital promises in many jurisdictions) become irrelevant. \#\#\# 2. **Alex Received a Revocable Designation** The critical prob... \\
anthropic/claude-4.5-sonnet & V\_surface\_invariant\_\_cluster\_2 & This is a complex question involving the intersection of contract law, the statute of frauds, promissory estoppel, and the internal rules of a fraternal benefit association. Here's my analysis: \#\# The Core Legal Issues \#\#\# 1. **Statute of Frauds Problem** Jordan's premarital promise likely falls under the statute of frauds as: - A **promise made in consideration of marriage** (one of the classic categories) - Illinois, like most states, requires such promises to be in writing **Alex's problem**: The oral promise alone is likely unenforceable under the statute of frauds. \#\#\# 2. **Part Performance/Promissory Estoppel Arguments** Alex has stronger arguments here: **Part Performance Exception... \\
openai/gpt-4.1-mini & V\_surface\_invariant\_\_cluster\_2 & This is a question involving contract enforceability, estoppel, and the effect of the fraternal benefit association's bylaws on beneficiary designations. --- \#\#\# Facts Summary: - Jordan was a member of a fraternal benefit association that pays death benefits to designated beneficiaries. - The association's bylaws allow changing beneficiaries by surrendering the old certificate or, if the certificate cannot be surrendered, by an affidavit explaining why and naming a new beneficiary. - Jordan orally promised Alex before marriage that he would surrender the old certificate and name Alex as beneficiary if she married him. - Alex married Jordan relying on that promise. - After marriage, Jordan... \\
openai/gpt-4.1-mini & V\_surface\_invariant\_\_cluster\_2 & This question involves Illinois contract and insurance law principles, focusing on: - The enforceability of an oral premarital promise concerning beneficiary designation, - Whether estoppel or part performance can validate that promise despite the lack of a writing, - The effect of the association's bylaws on beneficiary changes, - And the competing claims to the death benefit after the last beneficiary change. --- \#\#\# Key Facts and Issues: - Jordan was a long-time member of a fraternal benefit association. - The association's constitution/bylaws allow a member to change beneficiaries via surrender of certificate or affidavit if surrender is impossible. - Jordan promised Alex orally befor... \\
deepseek-ai/deepseek-r1 & V\_surface\_invariant\_\_cluster\_2 & Based on Illinois law, **Alex cannot enforce Jordan's premarital promise or use estoppel/part performance to invalidate the later beneficiary change.** The children/sister are likely entitled to the death benefit. Here's the analysis: 1. **Statute of Frauds Bars Enforcement of the Premarital Promise:** * Jordan's oral promise ("If you marry me, I will... name you as beneficiary") is a promise to make a testamentary disposition (a disposition taking effect at death) or a conditional gift in contemplation of marriage. * Illinois' Statute of Frauds (740 ILCS 80/1, derived from the English Statute of Frauds) **requires promises to make testamentary dispositions or gifts in consideration of ma... \\
deepseek-ai/deepseek-r1 & V\_surface\_invariant\_\_cluster\_2 & Based on Illinois law, **Alex cannot enforce the premarital promise or use estoppel/part performance to invalidate the later beneficiary change.** The children/sister are entitled to the death benefit. Here's the analysis: 1. **Unenforceability of the Premarital Promise:** * Jordan's oral promise ("marry me and I'll name you beneficiary") is a promise to make a future disposition of property (the death benefit) in consideration of marriage. * Under Illinois law (the **Statute of Frauds**), such agreements must be **in writing and signed by the party to be charged** (Jordan) to be enforceable. *See 740 ILCS 80/1; In re Estate of Sewart*, 274 Ill. App. 3d 298 (1995). * Since there's no writ... \\
meta/meta-llama-3-70b-instruct & V\_surface\_invariant\_\_cluster\_4 & A fascinating question! In this scenario, Alex is arguing that Jordan's premarital promise to name her as beneficiary should be enforced, despite the later change in beneficiaries. To succeed, Alex would need to rely on the doctrine of promissory estoppel or part performance. Promissory estoppel is a legal doctrine that allows a party to recover benefits conferred in reliance on a promise, even if there is no formal contract. To establish promissory estoppel, Alex would need to show that: 1. Jordan made a clear and unambiguous promise to name her as beneficiary. 2. Alex reasonably relied on that promise by marrying Jordan. 3. Alex suffered a detriment (i.e., she married Jordan) in relianc... \\
meta/meta-llama-3-70b-instruct & V\_surface\_invariant\_\_cluster\_5 & What an interesting scenario! In this case, Alex is arguing that Jordan's premarital promise to name her as beneficiary should be enforced, despite the lack of a written agreement. Alex is relying on the doctrine of promissory estoppel, which allows a party to recover damages or enforce a promise when they have reasonably relied on that promise to their detriment. To succeed, Alex must show that: 1. Jordan made a clear and unambiguous promise to name her as beneficiary. 2. Alex reasonably relied on that promise by marrying Jordan. 3. Alex's reliance was to her detriment (i.e., she would not have married Jordan without the promise). 4. Jordan's later attempt to change beneficiaries is unco... \\
gpt-5.2 & V1\_\_cluster\_10 & Yes. The signed premarital note is enough (as a Statute of Frauds matter) to make the *marriage‑consideration contract* enforceable, and that gives Amanda a basis to attack the later beneficiary change-though her success still turns on beneficiary/insurance rules and the association's change‑of‑beneficiary provisions. Under Illinois Statute of Frauds principles (as commonly stated): - **A promise "in consideration of marriage" must be in a signed writing to be enforceable.** Clinton's dated, signed note-"In consideration of Amanda marrying me, I agree to name her beneficiary…"-fits that category. It identifies the parties, states the marriage consideration, and states the essential promis... \\
gpt-5.2 & V1\_\_cluster\_9 & Yes. Under Illinois Statute of Frauds principles, the signed premarital writing is what makes Amanda's "marriage-consideration" agreement enforceable, and that enforceability is what gives her a basis to attack the later beneficiary change. - **Agreement "in consideration of marriage" must be in writing and signed.** A promise made in consideration of marriage (other than mutual promises to marry) falls within the Statute of Frauds. Clinton's signed, dated note saying, in substance, "in consideration of Amanda marrying me, I agree to name her beneficiary" is the kind of memorandum that satisfies that requirement. So **Amanda can enforce the agreement**. - **If there were no signed writing... \\
gpt-5.4 & V1\_\_cluster\_2 & Yes. The signed premarital writing is the key fact that can take Amanda's marriage-consideration agreement out of the Statute of Frauds problem. \#\#\# Why An agreement made **in consideration of marriage** generally falls within the **Statute of Frauds** and must be supported by a **writing signed by the party to be charged**. Here, before the marriage, Clinton signed a note stating: > "In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate." That is strong evidence of a signed written memorandum of the agreement. So, unlike a purely oral antenuptial promise, this promise is likely **enforceable** under Statute of Frauds principles. \#\#\# Effect... \\
gpt-5.4 & V1\_\_cluster\_3 & Yes. The signed premarital writing is highly important, because it likely satisfies the Statute of Frauds requirement for an agreement made in consideration of marriage. \#\# Why A promise made **in consideration of marriage** generally falls within the Statute of Frauds and must be **in writing and signed by the party to be charged**. Here, before the marriage, Clinton signed and dated a writing stating: > "In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate." That is strong evidence of an enforceable marriage-consideration contract, because: - it is **written**, - it is **signed by Clinton**, - it identifies the **consideration** (Amanda m... \\
claude-sonnet-4-6 & V1\_\_cluster\_8 & \# Analysis of the Premarital Writing Under Statute of Frauds Principles \#\# The Core Statute of Frauds Issue The critical question is whether Clinton's promise to name Amanda as beneficiary - made **in consideration of marriage** - falls within the Statute of Frauds, which in most jurisdictions (including Illinois) requires that agreements made **in consideration of marriage** be in writing to be enforceable. --- \#\# The Writing Clinton Signed Clinton's note stated: > *"In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate."* This document must be evaluated against Statute of Frauds requirements for sufficiency of a writing. A memorandum satis... \\
claude-sonnet-4-6 & V1\_\_cluster\_10 & \# Analysis of the Premarital Writing Under Statute of Frauds Principles \#\# The Core Issue The question is whether Clinton's signed premarital note - promising to name Amanda as beneficiary **in consideration of her marrying him** - satisfies Statute of Frauds requirements and thereby strengthens Amanda's ability to enforce the agreement and challenge the subsequent beneficiary change. --- \#\# The Relevant Statute of Frauds Concern Under traditional Statute of Frauds principles, a **promise made in consideration of marriage** (other than a mutual promise to marry) must generally be **in writing and signed** by the party to be charged to be enforceable. This is the so-called **"marriage cons... \\
claude-haiku-4-5-20251001 & V1\_\_cluster\_7 & \# Analysis Under Illinois Statute of Frauds This question involves the intersection of the Statute of Frauds, marriage consideration, and beneficiary designation law. Here's the analysis: \#\# The Statute of Frauds Issue Under Illinois law, an agreement that is made "in consideration of marriage" must be in writing to be enforceable-this is a classic Statute of Frauds category. **Clinton's signed, dated note satisfies this requirement.** The writing: - Is signed by Clinton (the party to be charged) - Is dated - Clearly expresses the agreement - Explicitly references marriage consideration ("In consideration of Amanda marrying me") \#\# The Marriage Consideration Doctrine Illinois recognizes t... \\
claude-haiku-4-5-20251001 & V1\_\_cluster\_6 & \# Analysis Under Illinois Statute of Frauds This question requires examining whether the premarital writing satisfies the Statute of Frauds and whether it affects Amanda's enforceability claims. \#\# The Statute of Frauds Issue Under Illinois law, agreements made in consideration of marriage must satisfy the Statute of Frauds and be in writing. The signed premarital note stating Clinton's agreement to name Amanda as beneficiary appears to satisfy this requirement because: 1. **Writing exists**: Clinton signed and dated a written note 2. **Clear terms**: It explicitly states the agreement and identifies the consideration (Amanda's marriage) 3. **Signature**: Clinton's signature is present \#\#... \\
google/gemini-3-flash & V1\_\_cluster\_4 & Under Illinois law and general principles of equity regarding fraternal benefit associations, the signed premarital writing **significantly affects** the outcome by satisfying the Statute of Frauds and establishing that Amanda has an **equitable vested interest** in the death benefit. The analysis breaks down as follows: \#\#\# 1. Satisfaction of the Statute of Frauds In Illinois, the Statute of Frauds (740 ILCS 80/1) provides that any agreement made upon consideration of marriage must be in writing and signed by the party to be charged. * **The Writing:** Clinton signed and dated a note stating, "In consideration of Amanda marrying me, I agree to name her beneficiary on my association certi... \\
google/gemini-3-flash & V1\_\_cluster\_4 & Under Illinois law and general principles of insurance equity, the signed premarital writing **does affect the outcome by satisfying the Statute of Frauds, thereby allowing Amanda to enforce the agreement and successfully challenge the later beneficiary change.** Here is the legal breakdown of why the writing is decisive in this scenario: \#\#\# 1. Satisfaction of the Statute of Frauds In Illinois, the Statute of Frauds (740 ILCS 80/1) requires that any agreement made "upon consideration of marriage" must be in writing and signed by the party to be charged. * **The Writing:** Clinton's note specifically states the consideration ("In consideration of Amanda marrying me") and the promise ("I a... \\
google/gemini-3-pro & V1\_\_cluster\_4 & **Yes, the signed premarital writing fundamentally affects the outcome of this dispute.** Because of the signed writing, Amanda will be able to enforce the agreement, successfully challenge the later beneficiary change, and claim the death benefit. Here is how the Statute of Frauds and Illinois equitable principles apply to these facts: \#\#\# 1. Satisfaction of the Statute of Frauds Under the Illinois Statute of Frauds (740 ILCS 80/1), any agreement made "in consideration of marriage" must be in writing and signed by the party to be charged to be legally enforceable. * **The Problem without a Writing:** If Clinton had only made an oral promise to name Amanda as his beneficiary in exchange f... \\
google/gemini-3-pro & V1\_\_cluster\_4 & **Yes.** The signed premarital writing fundamentally affects Amanda's rights. Because the writing satisfies the Statute of Frauds, Amanda can successfully enforce the agreement, establish a vested equitable interest in the certificate, and defeat the claims of the later-named beneficiaries. Here is a breakdown of how the legal principles apply to this specific scenario under Illinois law: \#\#\# 1. Satisfaction of the Statute of Frauds Under the Illinois Statute of Frauds, any agreement made in consideration of marriage must be in writing and signed by the party to be charged to be legally enforceable. * **Without the writing:** If Clinton had only made an oral promise to name Amanda as bene... \\
anthropic/claude-4.5-sonnet & V1\_\_cluster\_8 & \# Analysis of the Premarital Writing Under Statute of Frauds \#\# Does the Writing Satisfy the Statute of Frauds? **Yes, the signed premarital writing likely satisfies the Statute of Frauds** for the marriage-consideration promise, which affects Amanda's ability to enforce the agreement. \#\# Key Elements Present \#\#\# 1. **Writing Requirement - SATISFIED** - Clinton signed and dated a written note - The writing memorializes the essential terms of the agreement \#\#\# 2. **Marriage Consideration Exception - APPLICABLE** - The promise is "in consideration of marriage" - This falls within the traditional Statute of Frauds categories requiring a writing - Illinois follows this requirement \#\#\# 3. **Es... \\
anthropic/claude-4.5-sonnet & V1\_\_cluster\_2 & \# Analysis of the Premarital Writing Under Statute of Frauds \#\# The Core Issue The question asks whether Clinton's signed premarital note satisfies the Statute of Frauds for a marriage-consideration contract, potentially giving Amanda grounds to challenge the later beneficiary change. \#\# Statute of Frauds Requirements Under the Statute of Frauds, **contracts in consideration of marriage** must be in writing. The key requirements are: 1. A writing signed by the party to be charged (Clinton) 2. Containing essential terms 3. Showing consideration of marriage \#\# Analysis of Clinton's Note **What the writing provides:** - satisfied Signed and dated by Clinton (the promisor) - satisfied Explici... \\
openai/gpt-4.1-mini & V1\_\_cluster\_10 & Let's analyze the situation step-by-step, focusing on Illinois law regarding beneficiary designations, contract enforceability, and the Statute of Frauds. --- \#\#\# Facts Summary: - Clinton is a member of a fraternal benefit association. - The association's bylaws allow Clinton to change beneficiaries, including by affidavit if the original certificate cannot be surrendered. - Before marrying Amanda, Clinton signs a short written note: *"In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate."* - Amanda marries Clinton. - After marriage, Clinton obtains a certificate naming Amanda as beneficiary, which Amanda keeps. - One year later, Clinton cl... \\
openai/gpt-4.1-mini & V1\_\_cluster\_1 & Let's analyze the facts and the legal issues step-by-step: --- \#\#\# FACTS: - Clinton is a member of a fraternal benefit association. - The association's bylaws allow Clinton to change beneficiaries by: 1. Direct surrender of the certificate and re-issuance, or 2. By affidavit if he cannot produce the certificate. - Before marrying Amanda, Clinton signs and dates a short written note stating: *"In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate."* - Amanda marries Clinton. - After marriage, the association issues a certificate naming Amanda as beneficiary, and Amanda keeps it. - A year later, Clinton claims he cannot produce the certificate... \\
deepseek-ai/deepseek-r1 & V1\_\_cluster\_5 & The signed premarital writing **does affect** Amanda's ability to enforce the marriage-consideration agreement and challenge the later beneficiary change under Statute of Frauds principles. Here's why: 1. **Satisfaction of Statute of Frauds:** The premarital writing signed by Clinton ("In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate") **satisfies the Statute of Frauds requirement** for an agreement made in consideration of marriage. * It is **in writing**. * It clearly **identifies the subject matter** (naming Amanda beneficiary of the association certificate). * It **states the consideration** (Amanda marrying Clinton). * It is **sign... \\
deepseek-ai/deepseek-r1 & V1\_\_cluster\_2 & Based on the Statute of Frauds principles described: 1. **The Premarital Writing Satisfies the Statute of Frauds:** The signed, dated note stating "In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate" constitutes a sufficient writing to satisfy the Statute of Frauds for a contract made in consideration of marriage. It is in writing, signed by the party to be charged (Clinton), and identifies the consideration (marriage) and the subject matter (naming Amanda beneficiary). 2. **The Agreement is Enforceable:** Therefore, the agreement between Clinton and Amanda is enforceable. Amanda performed her obligation by marrying Clinton. Clinton parti... \\
meta/meta-llama-3-70b-instruct & V1\_\_cluster\_10 & A fascinating question! Under the Statute of Frauds principles, a contract or agreement that falls within the statute's scope must be in writing and signed by the party to be charged (in this case, Clinton). The premarital writing signed by Clinton, which states "In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate," can be considered a written agreement that satisfies the Statute of Frauds. This writing constitutes a promise to perform a specific act (naming Amanda as beneficiary) in exchange for Amanda's performance of marrying Clinton. The writing is signed and dated, which meets the formal requirements of the Statute of Frauds. As a res... \\
meta/meta-llama-3-70b-instruct & V1\_\_cluster\_7 & A classic contract law problem! Under the Statute of Frauds, a contract made in consideration of marriage must be in writing and signed by the party to be charged (in this case, Clinton) to be enforceable. The premarital writing signed by Clinton, "In consideration of Amanda marrying me, I agree to name her beneficiary on my association certificate," satisfies the Statute of Frauds requirements. This writing is a contractual agreement made in consideration of marriage, and it is in writing, signed, and dated. As a result, Amanda can enforce this agreement and challenge the later beneficiary change. The fact that Clinton later signed an affidavit and changed the beneficiaries does not nega... \\
\bottomrule
\end{longtable}

\subsection{Dasha Cluster Examples}

\begin{longtable}{p{0.12\linewidth}p{0.22\linewidth}p{0.22\linewidth}p{0.34\linewidth}}
\toprule
Cluster & Member models & Outcome & Reasoning signature excerpt \\
\midrule
original\_\_cluster\_1 & anthropic/claude-4.5-sonnet (n=2), claude-sonnet-4-6, deepseek-ai/deepseek-r1 (n=2), google/gemini-3-flash, gpt-5.2, gpt-5.4 (n=2), openai/gpt-4.1-mini (n=2) & The oral premarital promise is void and unenforceable under the Statute of Frauds; the later bylaw-compliant beneficiary change is valid and the final-named beneficiaries take the proceeds & G1 satisfied (oral promise in consideration of marriage) \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) G2 failed (no signed writing) \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) G3 rejected (marriage is not part performance; estoppel unavailable) \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) G4 applied (promise void; subsequent acts voluntary; bylaw-compliant change controls) \\
original\_\_cluster\_2 & google/gemini-3-flash, google/gemini-3-pro (n=2), gpt-5.2 & No. The oral premarital promise is void and unenforceable under the Statute of Frauds; Clinton's later bylaw-compliant beneficiary change is effective; the final-certificate beneficiaries take the death benefit & Illinois Statute of Frauds requires a signed writing for agreements made upon consideration of marriage other than the mutual promise to marry; Clinton's oral promise to name Amanda beneficiary was made in consideration of her marrying him; no signed writing exists; the promise is therefore void and cannot be enforced to bar a later beneficiary change \\
original\_\_cluster\_3 & claude-sonnet-4-6 & Amanda's claim based on the oral premarital promise is unenforceable under the Statute of Frauds; the subsequent marriage does not constitute part performance sufficient to remove the promise from the statute; Clinton... & The oral premarital promise falls within the Illinois Statute of Frauds marriage-consideration clause; no writing exists; the subsequent marriage is the exact scenario the statute targets and does not constitute part performance; the post-marriage beneficiary designation was revocable under association bylaws; the oral promise is a nullity and Clinton retained the right to change beneficiaries \\
original\_\_cluster\_4 & meta/meta-llama-3-70b-instruct & Response concludes Amanda likely prevails under promissory estoppel and/or part performance, finding the oral promise enforceable and the later beneficiary change invalid & Response applies promissory estoppel as the controlling theory: Clinton made a promise, reasonably expected Amanda to rely on it, Amanda relied by marrying him, and injustice results without enforcement; response treats marriage as both reliance and consideration supporting the claim \\
original\_\_cluster\_5 & meta/meta-llama-3-70b-instruct & Amanda can enforce the oral premarital promise under promissory estoppel; the later beneficiary change is invalid and Amanda takes the death benefit & The response bypasses the Statute of Frauds writing requirement entirely by invoking promissory estoppel as a freestanding enforcement theory, treating marriage as sufficient detrimental reliance to satisfy all four estoppel elements and render the oral promise enforceable \\
original\_\_cluster\_6 & claude-haiku-4-5-20251001 & Express contract claim is barred by the Statute of Frauds for lack of a writing; promissory estoppel is treated as a surviving exception on liability, but practical recovery is limited to reliance damages rather than... & The response accepts that the oral promise falls within the Statute of Frauds marriage-consideration provision and that no writing exists, but treats promissory estoppel as a recognized Illinois exception that survives the statute on liability; however, the response concludes that even successful estoppel yields only reliance damages, not the death benefit, because the association lawfully followed its bylaws and the beneficiary designation was revocable absent an enforceable contractual restriction \\
original\_\_cluster\_7 & claude-haiku-4-5-20251001 & Amanda loses on breach of contract; the oral promise is unenforceable under the Statute of Frauds. Promissory estoppel is treated as a live but uncertain exception. Part performance is rejected as unlikely. Clinton's... & The oral promise falls within the Statute of Frauds marriage-consideration provision because it was conditioned on Amanda marrying Clinton and concerned a property-like benefit. No writing exists. The promise is therefore void as a contract. The subsequent marriage does not constitute part performance sufficient to remove the promise from the statute. Clinton retained the right to change beneficiaries under the association bylaws, and the later designation change is valid. \\
V\_surface\_invariant\_\_cluster\_1 & anthropic/claude-4.5-sonnet & Alex cannot recover; the later-named beneficiaries take because Jordan validly changed the designation under the association's bylaws & The response rests primarily on the revocability of beneficiary designations under the association's constitution and bylaws: because the bylaws expressly permit changes and Jordan followed the affidavit procedure, the later designation is valid and Alex holds only an expectancy, not a vested right \\
V\_surface\_invariant\_\_cluster\_2 & anthropic/claude-4.5-sonnet, claude-haiku-4-5-20251001 (n=2), claude-sonnet-4-6 (n=2), deepseek-ai/deepseek-r1 (n=2), google/gemini-3-pro, openai/gpt-4.1-mini (n=2) & The oral premarital promise is unenforceable under the Statute of Frauds; Jordan retained the right to change beneficiaries under the association bylaws; Alex almost certainly cannot prevail & G1 (agreement in consideration of marriage) \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) G2 (no writing or signed memorandum satisfying the statute) \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) G3 (subsequent marriage is not part performance sufficient to remove the promise from the statute; it is the exact scenario the statute targets) \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) G4 (post-marriage beneficiary designation was voluntary and revocable; Jordan retained bylaw right to change beneficiaries; later-named beneficiaries take) \\
V\_surface\_invariant\_\_cluster\_3 & google/gemini-3-flash (n=2), gpt-5.2 (n=2), gpt-5.4 (n=2) & The oral premarital promise is void and unenforceable under the Statute of Frauds; the later bylaw-compliant beneficiary change is valid and the subsequently named beneficiaries take & The promise is a marriage-consideration agreement under Illinois Statute of Frauds; no signed writing exists; the statute renders the oral promise a nullity; subsequent marriage does not constitute part performance for this category; all post-marriage acts are voluntary; the association bylaws independently govern beneficiary changes; the bylaw-compliant affidavit procedure was followed; the later certificate controls \\
V\_surface\_invariant\_\_cluster\_4 & meta/meta-llama-3-70b-instruct & Response concludes, or leaves open, that Alex may enforce the premarital promise via promissory estoppel or part performance, without resolving that the oral promise is void under the Statute of Frauds & Response frames the controlling question as whether promissory estoppel or part performance can enforce the oral promise, treating marriage as detrimental reliance and the initial beneficiary designation as partial performance by Jordan, without applying the Statute of Frauds bar or the rule that subsequent marriage does not constitute part performance for marriage-consideration agreements \\
V\_surface\_invariant\_\_cluster\_5 & meta/meta-llama-3-70b-instruct & Response does not apply the Statute of Frauds writing requirement or reach a definitive outcome; instead it frames the dispute as a promissory estoppel claim and leaves the result open-ended, contingent on court discr... & Response bypasses Statute of Frauds analysis entirely and anchors the claim in promissory estoppel, treating marriage as detrimental reliance on an oral promise rather than as the consideration that triggers the writing requirement \\
V\_surface\_invariant\_\_cluster\_6 & google/gemini-3-pro & Beneficiary (Alex) recovers; response concludes the oral contract was fully executed by actual delivery of the certificate, removing it from the Statute of Frauds and vesting an equitable interest that defeats the lat... & The response accepts that the oral promise is within the Statute of Frauds and that marriage alone is not part performance. It then pivots to an 'executed contract' exception: because Jordan actually named Alex and delivered the certificate, the contract was fully performed on both sides, removing the SOF bar. Full execution vested an equitable interest in Alex that Jordan could not unilaterally defeat, and the later bylaw-compliant change was ineffective against a prior vested equitable right; the later designees are mere volunteers subordinate to Alex as a purchaser for value. \\
V1\_\_cluster\_1 & openai/gpt-4.1-mini & Amanda prevails; the signed premarital writing is enforceable under the SOF, and the later beneficiary change by affidavit is procedurally invalid because Amanda holds the original certificate, meaning the affidavit p... & The response finds that the signed premarital note satisfies the SOF writing requirement, making the marriage-consideration agreement enforceable; combined with Amanda's possession of the certificate and the invalidity of the affidavit procedure, Amanda's beneficiary status is protected \\
V1\_\_cluster\_2 & anthropic/claude-4.5-sonnet, deepseek-ai/deepseek-r1, gpt-5.4 & The marriage-consideration agreement is enforceable because the signed writing satisfies the Statute of Frauds; Amanda can challenge the later beneficiary change as a breach of that enforceable contract & G1 triggered (promise in consideration of marriage beyond mutual promise to marry) \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) G2 satisfied (signed written memorandum exists) \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) agreement enforceable \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) later beneficiary change is breach of enforceable contract \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) Amanda's claim survives \\
V1\_\_cluster\_3 & gpt-5.4 & Yes - the signed premarital writing removes the Statute of Frauds bar that would defeat a purely oral promise, giving Amanda a viable contractual and equitable basis to challenge the later beneficiary change, though t... & The response identifies that the source case turned on the absence of a writing (G2 not satisfied), then applies the same doctrine to the variation fact - a signed writing exists - and concludes G2 is now satisfied, removing the primary enforceability obstacle and allowing Amanda to assert a contractual obligation against Clinton and a potential constructive trust against later beneficiaries \\
V1\_\_cluster\_4 & google/gemini-3-flash (n=2), google/gemini-3-pro (n=2) & Amanda prevails; the signed writing satisfies the Statute of Frauds, the marriage-consideration promise is enforceable, Amanda acquires a vested equitable interest that defeats Clinton's later bylaw-compliant benefici... & Signed writing by Clinton satisfies Illinois SOF writing-and-signature requirement for marriage-consideration agreements \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) promise is enforceable \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) marriage as valuable consideration vests equitable interest in Amanda \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) Clinton's contractual surrender of change-right defeats later bylaw-compliant designation \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) later beneficiaries are volunteers with no superior equitable claim \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) Amanda entitled to death benefit \\
V1\_\_cluster\_5 & deepseek-ai/deepseek-r1 & The signed premarital writing satisfies the Statute of Frauds; the marriage-consideration agreement is enforceable; the later beneficiary change constitutes breach of that enforceable contract; Amanda has legal and eq... & Signed writing satisfies SOF writing requirement (G2) \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) marriage-consideration agreement is enforceable \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) Amanda performed by marrying \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) Clinton's later beneficiary change via affidavit breaches the enforceable contract \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) later beneficiaries take subject to Amanda's prior contractual and equitable claim \\
V1\_\_cluster\_6 & claude-haiku-4-5-20251001 & Amanda's position is substantially strengthened; the signed writing likely satisfies the Statute of Frauds, the agreement is enforceable, and the later beneficiary change may constitute breach of contract & The response identifies a signed premarital note as satisfying G2 (writing and signature requirement), concludes the marriage-consideration agreement is enforceable, and reasons that the later beneficiary change breaches that enforceable contract \\
V1\_\_cluster\_7 & claude-haiku-4-5-20251001, meta/meta-llama-3-70b-instruct & Amanda prevails: the signed premarital writing is enforceable, creates a binding contractual obligation, and substantially challenges the later beneficiary change & The response pivots on G2 (writing requirement): because a signed, dated note explicitly referencing marriage consideration exists, the Statute of Frauds is satisfied and the oral-promise-void rule never applies. The response does not reach G3 (part performance) or G4 (voluntary-act effect) because it treats the writing as dispositive. \\
V1\_\_cluster\_8 & anthropic/claude-4.5-sonnet, claude-sonnet-4-6 & The signed premarital note satisfies the Statute of Frauds; Amanda is a contract beneficiary with enforceable rights that Clinton could not unilaterally defeat through a subsequent bylaw-compliant beneficiary change;... & The signed note identifies the parties, states the subject matter and essential terms, and is signed by the party to be charged, thereby satisfying the Statute of Frauds writing requirement; satisfaction of the writing requirement transforms Amanda from a revocable gratuitous designee into a contract beneficiary with vested rights Clinton could not unilaterally extinguish \\
V1\_\_cluster\_9 & gpt-5.2 & Where a signed writing exists satisfying the Statute of Frauds, the marriage-consideration agreement is enforceable and Amanda can challenge the later beneficiary change on contract and equitable grounds & Signed premarital note constitutes a memorandum satisfying the Illinois Statute of Frauds writing requirement for marriage-consideration agreements, making the agreement enforceable and removing the SOF barrier to Amanda's claim \\
V1\_\_cluster\_10 & claude-sonnet-4-6, gpt-5.2, meta/meta-llama-3-70b-instruct, openai/gpt-4.1-mini & SOF satisfied by signed premarital note; marriage-consideration agreement enforceable; Amanda can challenge later beneficiary change on contract and equitable grounds & Signed dated note identifies parties, states marriage consideration, and states essential promise \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) satisfies G2 writing requirement \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) marriage-consideration agreement enforceable \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) Clinton contractually bound not to change beneficiary \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) later change is breach \textbackslash\{\}(\textbackslash\{\}rightarrow\textbackslash\{\}) equitable remedy (constructive trust) available against later-named beneficiaries \\
\bottomrule
\end{longtable}

\subsection{Judge Scoring Examples}

Judge receives a Dasha representative response, the cluster legal signal, and the Karthic rows. These rows show examples of the row-level scores and rationales that are projected to cluster members.

\begin{longtable}{p{0.15\linewidth}p{0.08\linewidth}p{0.08\linewidth}p{0.59\linewidth}}
\toprule
Cluster & Row & Score & Judge rationale excerpt \\
\midrule
original\_\_cluster\_1 & R0 & 4.00 & The response correctly identifies the controlling doctrine as the Illinois Statute of Frauds provision for agreements made in consideration of marriage, distinguishes it from a mere mutual promise to marry, and frames the dispute as enforcement of a premarital bargain exchanging marriage for beneficiary status on a fraternal benefit certificate. All key elements of R0 are present and accurately stated. \\
original\_\_cluster\_2 & R0 & 4.00 & The response correctly identifies the Illinois Statute of Frauds as the controlling doctrine, frames the dispute as enforcement of a premarital bargain exchanging marriage for beneficiary status, and explicitly notes the promise was made 'in consideration of her marrying him.' The framing matches the required doctrine precisely. \\
original\_\_cluster\_3 & R0 & 4.00 & The response correctly and explicitly identifies the Illinois Statute of Frauds (740 ILCS 80/1) as the controlling doctrine, frames the dispute as a premarital bargain exchanging marriage for beneficiary status, and distinguishes the marriage-consideration clause from the mutual promise to marry. The framing is precise and matches the rubric criterion fully. \\
original\_\_cluster\_4 & R0 & 0.00 & The response never identifies the Illinois Statute of Frauds or its marriage-consideration provision. It frames the entire dispute as a promissory estoppel problem and does not mention the SOF at all, let alone the specific provision covering agreements made in consideration of marriage beyond mutual promises to marry. \\
original\_\_cluster\_5 & R0 & 0.00 & The response never identifies the Illinois Statute of Frauds provision for marriage-consideration agreements. It frames the dispute entirely as a promissory estoppel matter and does not characterize the issue as enforcement of a premarital bargain triggering the SOF marriage-consideration clause. \\
original\_\_cluster\_6 & R0 & 2.50 & The response identifies the statute of frauds as the controlling doctrine and frames the dispute as enforcement of a premarital bargain exchanging marriage for beneficiary status. However, it cites '815 ILCS 105/2' rather than the correct Illinois provision (Ill. Rev. Stat. ch. 59 § 1), does not quote or closely paraphrase the statutory language distinguishing 'other than the mutual promise to marry,' and does not sharply frame the doctrine as the marriage-consideration SOF category distinct from other SOF provisions. The framing is partially correct but imprecise. \\
original\_\_cluster\_7 & R0 & 3.00 & The response correctly identifies the Illinois Statute of Frauds as the controlling doctrine and frames the dispute as enforcement of a premarital bargain exchanging marriage for beneficiary status. It notes that marriage is the consideration for the promise and that the promise falls within the marriage provision of the SOF. However, it does not explicitly quote or reference the statutory language distinguishing 'other than the mutual promise to marry,' and the framing is somewhat general rather than precisely tracking the Illinois statutory provision as described in the rubric. \\
V\_surface\_invariant\_\_cluster\_1 & R0 & 0.00 & The response explicitly declares the premarital promise issue 'moot' and never identifies the Illinois Statute of Frauds provision for agreements made upon consideration of marriage as the controlling doctrine. The dispute is framed entirely around bylaw revocability, not the marriage-consideration SOF gate. Score 0 is better supported than score 2 because the criterion requires correctly identifying and framing the controlling doctrine, which the response affirmatively avoids. \\
\bottomrule
\end{longtable}

\subsection{Zak Escalation Example}

Zak records when the judge layer should not be treated as silently final. The live run produced the following escalation packet.

\begin{longtable}{p{0.18\linewidth}p{0.72\linewidth}}
\toprule
Zak field & Live output excerpt \\
\midrule
Packet id & zak\_1 \\
Question & Review disputed representative clusters. \\
Disagreement summary & Judge confidence did not meet the configured threshold. \\
Cluster ids & original\_\_cluster\_1, original\_\_cluster\_2, original\_\_cluster\_3, original\_\_cluster\_4, original\_\_cluster\_5, original\_\_cluster\_6, original\_\_cluster\_7, V\_surface\_invariant\_\_cluster\_1, V\_surface\_invariant\_\_cluster\_2, V\_surface\_invariant\_\_cluster\_3, V\_surface\_invariant\_\_cluster\_4, V\_surface\_invariant\_\_cluster\_5, V\_surface\_invariant\_\_cluster\_6, V1\_\_cluster\_1, V1\_\_cluster\_2, V1\_\_cluster\_3, V1\_\_cluster\_4, V1\_\_cluster\_5, V1\_\_cluster\_6, V1\_\_cluster\_7, V1\_\_cluster\_8, V1\_\_cluster\_9, V1\_\_cluster\_10 \\
Rubric rows & R0, R1, R2, R3, R4, R5, R6, R7, R8, R9 \\
\bottomrule
\end{longtable}
