\section{Contributions and Claim Map}

The pipeline is intended to be understandable as a research instrument, not only
as a software demo. Its main contribution is an automated source-to-ranking
method that evaluates legal reasoning paths rather than isolated answer strings.
The method is novel in four connected ways. First, the benchmark is generated
from a source case rather than from a static hand-authored question. Second, the
rubric is generated dynamically from the locked source packet instead of reused
as a generic checklist. Third, responses are compressed by legal reasoning
signature before judging, so the scored unit is a centroid representing a line of
legal reasoning. Fourth, the judge projects centroid scores back to all cluster
members, producing model rankings while preserving row-level rationales and
escalation state.

\begin{tabular}{p{0.20\linewidth}p{0.25\linewidth}p{0.25\linewidth}p{0.20\linewidth}}
\toprule
Claim & Implementation & Why it is distinctive & Current evidence \\
\midrule
Source-grounded benchmark generation & Frank reads a source case plus canonical instruction context and emits a versioned JSON packet with doctrine gates, source extraction, gold answer, neutral question, variations, and controller card & The question, gold answer, and variations are derived from the same source artifact rather than manually patched after model outputs are seen & Live natural-response batch begins from one source case and produces a complete Frank packet with prompt and source hashes \\
Dynamic legal rubric generation & Karthic consumes only the locked Frank packet and instruction context, then emits weighted source-supported rubric rows with schema repair and category normalization & The rubric is case-specific and source-grounded, not a reusable generic legal-quality rubric & Live run produced 10 Karthic rows across required categories and passed validation gates \\
Reasoning-path clustering & Dasha extracts reasoning signatures from model answers, normalizes them into legal-reasoning buckets, and clusters unlabeled responses after generation & The pipeline compresses answers by legal theory, not by surface wording or known labels supplied to the response generator & Natural-response audit clustered 9 unlabeled answers to one Frank question into 1 shared wife/certificate reasoning centroid \\
Centroid judging and projection & Judge scores one representative per Dasha cluster row-by-row against Karthic, then projects the weighted centroid score to all cluster members & The method reduces judging cost and makes rankings explainable through cluster-level legal rationales & Live run produced 10 row-level judge scores and projected scores to 9 responses across 3 model identifiers \\
Escalation visibility & Zak creates packets only when uncertainty, disagreement, or quality thresholds fail & Failures become explicit research artifacts rather than silent exclusions & Live run recorded no escalation needed; validator still checks that escalation state exists \\
\bottomrule
\end{tabular}

\subsection{Statute-of-Frauds Litmus Test}

Statute of Frauds is the first litmus domain because it naturally contains
discrete legal gates and boundary facts: marriage consideration, one-year
performance, suretyship, land interests, goods/UCC writings, executor or
administrator promises, writing substitutes, and equitable exceptions. That
structure makes it a useful early test for whether an automated pipeline can
generate legally meaningful variations and separate different reasoning paths.

The current evidence is strongest for pipeline mechanics and for representative
Statute-of-Frauds reasoning paths. The live model batch validates the full
source-to-ranking path on a marriage-consideration beneficiary-certificate case.
The 500-response regression suite then checks the Dasha clustering container
against eight Statute-of-Frauds archetypes: wife/certificate enforcement,
association replacement-certificate control, one-year/no-writing bar,
one-year-under-year enforceability, suretyship/main-purpose exception, land
part-performance, goods/UCC quantity defect, and executor personal-promise
without writing. This does not prove every possible Statute-of-Frauds case is
solved, but it shows that the pipeline's schemas, clustering machinery, and
validation surfaces cover the major gate families needed for that domain.

\subsection{Generalization Beyond Statute of Frauds}

The architecture is doctrine-general because every live stage is driven by the
source case and canonical instruction context. Frank is asked to infer the
doctrine and legal gates; Karthic builds a rubric from the locked Frank packet;
Dasha normalizes whatever doctrine, trigger, outcome, and exception structure is
present in the responses; Judge scores against Karthic's rows rather than a
Statute-of-Frauds-specific checklist. To apply the method to another legal
field, the expected change is not the pipeline architecture but the instruction
context and calibration examples supplied to the agents. Broader legal-domain
claims therefore require additional source packs and held-out cases, but the
pipeline is already structured so those additions are data and instruction
extensions rather than a new evaluation system.
