\section{Introduction}

Legal evaluation datasets usually expose models to a fixed prompt and then
compare each answer with a reference answer or aggregate score. That design is
often too coarse for legal reasoning. Two answers can reach the same bottom line
through different doctrinal gates; two answers can cite the same doctrine but
apply different exceptions; and two answers can discuss the same facts while
resting on different legal theories. A legal benchmark therefore needs to
measure reasoning paths as well as final outcomes.

We study source-grounded legal reasoning evaluation. The input is a citable
legal source case, not a manually authored hypothetical. The output is a
complete evaluation bundle: a source-derived benchmark question, a gold answer,
controlled factual perturbations, a case-specific rubric, natural model
responses, reasoning-path clusters, centroid-level judge scores, projected
member scores, model rankings, and escalation records. This formulation makes
benchmark construction, response clustering, judging, and ranking part of one
reproducible protocol rather than a sequence of informal manual decisions.

The reported implementation uses named LLM modules as artifact generators.
Frank converts the source case into a benchmark packet. Karthic converts that
packet into scored rubric rows. Response models answer the generated question
without a system prompt or forced answer schema. Dasha abstracts each answer
into a legal-reasoning signature and clusters signatures into centroids. Judge
scores each centroid against Karthic's rubric, and Zak records cases where
uncertainty or disagreement prevents silent acceptance of the score. All module
inputs, prompt hashes, outputs, and validation checks are serialized.

Statute of Frauds is the calibration domain for this paper because it has
discrete doctrinal gates, boundary facts, and plausible alternative reasoning
paths: marriage consideration, one-year performance, signed-writing compliance,
suretyship, land, goods, executor promises, and equitable exceptions. The
architecture itself is not Statute-of-Frauds-specific. The live path asks Frank,
Karthic, and Dasha to infer doctrine, gates, rubric rows, and reasoning
signatures from the source case and instruction stream. Statute of Frauds is
therefore used as a litmus test for the general source-to-rubric-to-centroid
method.

This paper makes a bounded methodological claim. We do not claim that the
pipeline has established external legal validity across legal domains. We claim
that the pipeline can be implemented as a reproducible artifact-generating
method and that, on a real Statute-of-Frauds case study, it produces inspectable
outputs at every stage: source-grounded Frank artifacts, a case-specific Karthic
rubric, natural multi-model responses, perturbation-aware Dasha clusters,
row-level judge scores, projected model rankings, and Zak escalation state.
The appendices include direct excerpts from the live run bundle so that the
reader can inspect the practical artifact quality rather than relying only on
aggregate tables.
