\section{Limitations}

This manuscript reports internal validation, not expert-reviewed legal validity.
The live validation run is bounded and should be interpreted as an internal
source-to-ranking validation, not a population-level benchmark of model
performance. The natural-response Dasha audit confirms that the clustered inputs
are model answers to Frank-generated question tracks rather than responses
generated from preassigned labels, and the reported run produced 15 observed
track-aware reasoning clusters over 60 answers. That is a meaningful internal
Dasha result, but it is still a single-case batch. It does not establish that
arbitrary live model outputs will always produce stable or legally correct
clusters. The
500-response scale result is a controlled regression test with known reasoning
signatures, not a claim that arbitrary live model outputs will always produce
perfectly separable clusters. The evidence is therefore strong for pipeline
mechanics and internal reproducibility, but still bounded for external legal
validity and cross-doctrine generalization.

The Statute-of-Frauds evidence should be read as a strong litmus test, not as an
exhaustive doctrinal proof. The live run validates one source-to-ranking case,
and the regression suite covers eight major Statute-of-Frauds reasoning
archetypes. A claim that the system handles every Statute-of-Frauds fact pattern
would require a larger held-out case suite across jurisdictions, transaction
types, writing forms, and exception doctrines.

The reported live model roster is broader than a smoke test but still bounded.
The manuscript validates the path with ten model identifiers over three tracks;
broader model-family claims require larger rosters, more repeated samples,
held-out cases, and natural-response batches where multiple models
independently converge on or diverge from the same legal reasoning paths.

The instruction corpus is deepest for Statute of Frauds. The live agents are now
given a doctrine-general protocol and must infer doctrine from the source, but
other doctrine families will need richer pack-specific examples before external
claims should be made about broad legal coverage.

LLM-as-judge methods are known to have bias risks, including position,
verbosity, and self-preference biases
\cite{zheng2023judging,shi2024positionbias,wataoka2024selfpreference}. The
pipeline mitigates some of these risks by using row-level rubrics, source
support, centroid-level scoring, a two-model judge panel, and adjudication for
unstable panel rows, but future validation should include larger judge
ensembles, repeated scoring across held-out cases, rubric ablation,
model-separated judges, and comparison to expert labels.

Finally, the reported Karthic artifact materializes the scoring core of the
rubric row card rather than every field described in the instruction spec. The
paper is therefore careful to claim automated row-level scoring, source support,
category coverage, and non-duplication checks, not full automation of every
human-facing row-card annotation that a legal research team may want before
external submission.
