\section{Methods}

\subsection{Pipeline Overview}

The implementation is a Python research harness under
\texttt{research/validation/} with a minimal Next.js workbench used only for
running and inspecting artifacts. Runs are controlled by JSON configuration
files that specify a source-case path, output directory, model identifiers,
sample counts, temperatures, quality gates, clustering method, and judge
settings. The harness writes every stage artifact as JSON: Frank packet, Karthic
rubric, model responses, Dasha clusters, judge scores, Zak packets, manifest,
Markdown report, validation summaries, and paper tables. This design was chosen
so that the research claim is reproducible from files rather than from an
interactive UI session.

The pipeline has five named stages. Frank ingests a source case and produces a
doctrine-aware benchmark packet. Karthic generates a rubric from the locked
Frank packet. Dasha clusters generated model responses by legal reasoning
signatures. Judge scores Dasha centroids against Karthic rows and projects those
scores to all members of each cluster. Zak produces escalation packets when
uncertainty or disagreement warrants further review. The stages communicate only
through serialized artifacts, which makes each boundary auditable and testable.

\subsection{Model-Call and Provenance Layer}

All live LLM calls use a small JSON-over-HTTP client rather than a framework
agent runtime. The model-call layer has two functions: \texttt{generate\_text}
for ordinary completions and \texttt{generate\_json} for strict JSON-producing
agents. When an agent returns malformed JSON, \texttt{generate\_json} attempts a
repair pass and then re-parses the result. This keeps Frank, Karthic, Dasha, and
Judge on explicit schemas instead of free-form prose.

Every run records provenance at three levels. First, source text is hashed with a
short SHA-256 content hash. Second, each live prompt bundle is hashed after
including the instruction context and agent settings. Third, generated responses
record model identifier, sample index, question id, answer-format instruction,
timestamp, and text. The purpose is not merely bookkeeping: prompt hashes make it
possible to distinguish a substantive methodological change from a repeated run
under the same frozen instructions.

\subsection{Instruction Context}

Frank, Karthic, and Dasha each load bounded instruction context from the
\texttt{instructions/} tree at runtime. The first file for all three agents is a
cross-agent legal reasoning protocol stating that Statute of Frauds is a
calibration domain, not a hard-coded assumption. Additional agent-specific files
provide Frank source-to-question instructions, Karthic rubric instructions, and
Dasha evaluation instructions. The loaded context is included directly in the
agent prompt and hashed into the output artifact. This was added to prevent the
live path from silently depending on old deterministic Statute-of-Frauds logic.

\subsection{Frank: Source-to-Benchmark Generation}

Frank receives the source case text and is instructed to infer the doctrine,
legal gates, material facts, source limits, neutral question, gold answer, and
boundary variations. The gold answer uses a consistent structure: jurisdiction
assumption, bottom-line outcome, controlling doctrine, transaction
characterization, writing or element trigger, compliance or exception analysis,
other defenses, and strongest counterargument. This structure is doctrine-aware:
for non-Statute-of-Frauds cases, the heading content should map to the
appropriate doctrinal elements rather than force an irrelevant writing analysis.
The live Frank prompt loads the canonical instruction tree, including the
cross-agent general legal reasoning protocol, and expressly treats Statute of
Frauds as a calibration domain rather than a default doctrine.

Technically, Frank returns strict JSON with fields
\texttt{doctrine\_family}, \texttt{detected\_doctrine\_gates},
\texttt{source\_extraction}, \texttt{neutral\_question}, \texttt{gold\_answer},
\texttt{variations}, and \texttt{controller\_card}. The implementation then
wraps that output in a versioned \texttt{research.frank.llm.v1} packet, attaches
source and prompt hashes, and promotes \texttt{controller\_card.primary\_gate\_id}
as the downstream control field. A backward-compatible
\texttt{statute\_of\_frauds} object is emitted only when the inferred doctrine is
actually Statute of Frauds. The reason for this schema is that later stages
should depend on explicit source-grounded doctrine gates rather than on hidden
prompt assumptions.

\subsection{Karthic: Dynamic Rubric Construction}

Karthic builds a fresh rubric for every locked Frank packet. The required rubric
coverage includes doctrine or gate, rule or element, facts, compliance,
exceptions or defenses, counterarguments, conclusion, variation sensitivity, and
source support. Rows include identifiers, categories, weights, criteria, and
source-support snippets. Category normalization is applied after LLM generation
so semantically equivalent labels such as ``doctrine/gate'' and
``doctrine\_gate'' map to the canonical category ``doctrine.''

The rubric artifact is versioned as \texttt{research.karthic.llm.v1}. Karthic is
asked for a top-level \texttt{rows} array, but the parser also accepts common LLM
output shapes such as \texttt{rubric.rows}, \texttt{base\_rubric.rows}, and
module-level row arrays. If the first rubric fails minimum row count or required
category checks, the harness runs a strict repair prompt requiring at least the
configured number of rows, required categories, source-grounded criteria, row
ids, weights, and source-support fields. If weights do not sum to one, they are
renormalized across rows. This repair step is engineering calibration, not a
research claim; the frozen artifact still records the final prompt hash and row
schema.

\subsection{Response Generation}

The pipeline evaluates a roster of concrete model identifiers. The current
implementation can route calls through different execution backends, but the
research unit is the model output, not the backend used to obtain it. Every
model receives the same Frank-generated question and answer-format instruction.
Each response records the model identifier, sample index, timestamp, question
id, answer format, and prompt provenance.

The live natural-response batch used the same Frank question for all response
models. The answer prompt included the source excerpt, the neutral legal
question, and a fixed heading order. Temperature is controlled in the run config
and offset slightly across repeated samples from the same model to induce
natural answer variation without changing the question or rubric. No response is
given a target reasoning label before generation.

\subsection{Dasha: Reasoning-Signature Clustering}

Dasha extracts a normalized reasoning signature from each response. The live
signature includes doctrine, issue, rule trigger, outcome, exception or defense,
reasoning path, conclusion, and key distinguishing facts. The first version of
the live clustering grouped by near-exact signature strings, which over-split
paraphrases. The current implementation therefore converts each LLM-generated
signature into a compact bucket tuple:
\texttt{(doctrine\_bucket, trigger\_bucket, outcome\_bucket,
exception\_bucket, reasoning\_version)}. For the current Statute-of-Frauds
calibration case, this distinguishes marriage-beneficiary-certificate reasoning,
later-beneficiary/replacement-control reasoning, one-year reasoning, suretyship
reasoning, land-interest reasoning, and goods/UCC reasoning when those paths are
present. The same mechanism falls back to normalized source-derived terms for
non-SOF doctrines.

Responses with the same normalized bucket tuple are grouped into clusters. Each
cluster has a representative centroid, member ids, centroid/member consistency
metrics, and a legal signal summary. The representative response is selected by
maximizing a combination of token-level Jaccard similarity and feature-match
similarity against other members. Mean text similarity is retained as a warning
signal, not as the clustering key, because legally equivalent answers often use
different surface language. Deterministic Statute-of-Frauds keyword clustering
remains only as an offline regression fallback when no LLM reasoning signatures
exist.

\subsection{Judge and Zak}

The judge applies every Karthic rubric row to each Dasha centroid and returns a
0--4 score with rationale. The centroid's weighted score is projected to all
responses in the cluster, enabling model-level rankings. This follows the
rubric-conditioned LLM-as-judge pattern in prior work while avoiding pairwise
comparisons across every individual response. Zak receives judge and cluster
signals and emits an escalation packet only when configured uncertainty,
disagreement, or quality failures require further review.

The judge receives the cluster legal signal, the representative response, and a
compact copy of every Karthic row. It must return one row score for every rubric
row. Scores are clipped to the 0--4 range and combined using the rubric weights.
The resulting centroid score is copied to every response in that cluster. Model
rankings are then computed as the mean projected score for each model identifier.
This projection rule is why a run with one Dasha cluster can produce tied model
rankings: if all models use the same legal reasoning path, the method treats the
centroid as the scored unit. Zak is intentionally simple in the current
implementation: if judge agreement or quality thresholds fail, it emits a packet
containing the disputed cluster ids and rubric row ids; otherwise it records that
no escalation was required.
