\section{Internal Results}

\subsection{Live Source-to-Ranking Run}

The claim-supporting source input is a real court-case PDF, not a synthetic
hypothetical or a manually written fact summary. The current Statute-of-Frauds
calibration case is \emph{Anglemire v. Policemen's Benevolent Association of
Chicago}, 301 Ill. App. 277, 22 N.E.2d 713 (Ill. App. Ct. 1939). The run
configuration points to the stored PDF under
\texttt{cases/MarriageSoF\_Anglemire v Policemens Benev Assn of Chicago.pdf};
the protocol-freeze artifact records the PDF content hash, extracted-text hash,
case id, citation, jurisdiction, court, decision date, and source limitations.
This matters methodologically because Frank must derive the benchmark from a
citable source authority, not from a reconstructed scenario supplied by the
researcher.

The live LLM-driven pipeline was run on that real Statute of Frauds calibration
case using ten response model identifiers with two samples per question track:
\texttt{gpt-5.2}, \texttt{gpt-5.4}, \texttt{claude-sonnet-4-6},
\texttt{claude-haiku-4-5-20251001}, \texttt{google/gemini-3-flash},
\texttt{google/gemini-3-pro}, \texttt{anthropic/claude-4.5-sonnet},
\texttt{openai/gpt-4.1-mini}, \texttt{deepseek-ai/deepseek-r1}, and
\texttt{meta/meta-llama-3-70b-instruct}. Frank and Karthic used
\texttt{gpt-5.2}. Dasha used LLM reasoning signatures, and Judge used a
two-model \texttt{gpt-5.2}/\texttt{claude-sonnet-4-6} panel with adjudication
for unstable rows.

The run used the corrected natural response protocol: each response model
received only the Frank-generated question, with no system prompt, no hidden
gold answer, and no required memo headings. The run produced 60 model responses
over the original, invariant, and material question tracks; 10 rubric rows; 22
Dasha clusters; 220 final row-level judge scores; adjudicated final centroid scores;
60 projected member scores; and 10 model ranking entries. Table
\ref{tab:internal-validation}
summarizes the resulting stage checks.

\begin{table}[h]
\centering
\caption{Internal validation summary for the live natural-response batch.}
\label{tab:internal-validation}
\input{tables/internal_validation_summary}
\end{table}

This live run is intentionally bounded to control cost. Its purpose is not to
estimate population-level model performance with narrow confidence intervals.
It demonstrates that the real model-generation path runs from source case to
model ranking without manual patching, and that Dasha can separate multiple
observed legal-reasoning paths in a perturbation-aware natural-response batch.

\subsection{Natural-Response Dasha Audit}

The relevant Dasha test is whether responses are clustered after models answer
the same Frank-generated question. The live audit therefore checks the completed
run bundle for unlabeled model answers, the expected Frank question tracks, full
cluster coverage, and no preassigned reasoning labels. Table
\ref{tab:natural-dasha-audit} summarizes that audit.

\begin{table}[h]
\centering
\caption{Natural-response Dasha audit for the live model batch.}
\label{tab:natural-dasha-audit}
\input{tables/natural_response_audit}
\end{table}

This audit is intentionally separate from the deterministic stress suite. It is
the evidence that Dasha is operating on model outputs rather than on categories
given to the response generator. In this batch, the normalized Dasha signatures
formed 22 track-aware clusters. On the original and invariant tracks, the
dominant cluster family rejected enforcement of the unwritten marriage-
consideration promise and let the later bylaw-compliant designation control.
Minority clusters captured equitable override, constructive-trust, and
certificate-as-writing theories. On the material signed-writing track, the
dominant answer family shifted toward enforceability or written-compliance
reasoning. The audit therefore passes the configured divergence and
perturbation gates, while still remaining too small to support broad claims
about all models or all Statute-of-Frauds cases.

\begin{table}[h]
\centering
\caption{Dasha cluster summary for the live natural-response run.}
\label{tab:dasha-cluster-summary}
\input{tables/dasha_cluster_summary}
\end{table}

\begin{table}[h]
\centering
\caption{Projected model rankings from centroid scores.}
\label{tab:model-rankings}
\input{tables/model_rankings}
\end{table}

\subsection{Dasha Multi-Path Audit}

The live Anglemire responses also exposed a Dasha-specific representation
issue: natural legal answers often discuss several gates or equitable theories
before settling on one. Regenerating Dasha signatures with explicit
primary-path and secondary-path fields completed for all 60 saved responses
without malformed JSON failures. A first pass that clustered on every
secondary path overfragmented into 49 clusters. The tuned rule preserves the
full secondary-path audit profile but clusters only on accepted or uncertain
non-primary paths. After repairing a negative-language normalization error
around words such as ``unenforceable,'' the full source-to-score rerun produced
22 track-aware clusters: 6 on the original question, 8 on the
surface-invariant edit, and 8 on the material signed-writing edit. Judge scored
those 22 centroids with a two-model panel, yielding 44 panel calls, 220 final
row-level scores, 11 adjudications, projected member scores for all 60
responses, and updated model rankings. The most common cluster profile remained
no material secondary path, but the audit also captured uncertain
promissory-estoppel or reliance analysis, accepted part-performance analysis,
accepted reliance analysis, and accepted signed-writing analysis.

\subsection{Question Perturbation Validation}

The perturbation loop was added as a separate validation lane. Frank variations
are converted into executable question tracks, responses retain their
\texttt{track\_id}, Dasha clusters each track separately, and the perturbation
report compares each variant's dominant reasoning signal against the original
question. Table \ref{tab:perturbation-validation} shows the reported live
perturbation run: a surface party-name edit preserved the original dominant
answer path, while a material signed-writing edit changed the dominant answer
path.

\begin{table}[h]
\centering
\caption{Perturbation validation for the live model batch.}
\label{tab:perturbation-validation}
\input{tables/perturbation_validation_summary}
\end{table}

\subsection{Controlled 500-Response Dasha Regression Test}

The 500-response suite is now treated as a deterministic regression test rather
than a robustness demonstration. It generates fixture answers across eight
legally distinct Statute-of-Frauds reasoning archetypes so the software can test
cluster bookkeeping, centroid projection, table generation, and metrics at the
target scale. It does not show that Dasha can discover reasoning families from
natural model outputs.

\begin{table}[h]
\centering
\caption{Controlled Dasha clustering regression test.}
\label{tab:stress-validation}
\input{tables/internal_stress_summary}
\end{table}

The regression test produced eight observed clusters for eight expected reasoning
archetypes. Cluster purity, cluster completeness, and macro-F1 were all 1.0.
This proves that the clustering layer preserves normalized legal-reasoning
distinctions at the target 500-response scale when the signatures are already
known. It does not substitute for the natural-response audit; instead, it
functions as a regression and scale test for cluster bookkeeping, centroid
projection, and metrics generation.

\subsection{Internal Test Coverage}

The reference implementation has 77 research-pipeline tests covering offline run-bundle
exports, Frank packet quality, Karthic rubric quality, SOF gate regression
cases, Dasha clustering invariants, sparse-response gate context, LLM reasoning
signature clustering, source-derived Dasha gate aliasing, a non-SOF
contract-interpretation transfer smoke, judge projection and model ranking,
low-margin Zak escalation, repeated-judge and panel-judge stability aggregation,
Dasha member/centroid audit generation, protocol-freeze manifests, manuscript reference and hygiene linting, model roster config loading, model-call polling, natural-response audit
generation, live-config preflight, credential-alias checks, live-call budget caps, runtime budget enforcement, run-bundle integrity auditing, secret and local-path linting, internal review packet generation, claim-ledger generation, handoff-manifest generation, consolidated no-call audit, method-readiness reporting, review-readiness table generation, metrics, perturbation-track generation, perturbation reporting, and
internal stress-table generation. These tests make the pre-expert-review
manuscript reproducible: the reported claims are backed by executable checks
rather than by visual inspection alone.
