\section{Technical Review Readiness}

This manuscript is ready for technical review in the following sense:
the pipeline now has a complete fresh live run under the natural response
protocol, executable validation checks, regenerated paper tables, and a run
bundle containing Frank, Karthic, Dasha, Judge, Zak, response, manifest, and
hash artifacts. The paper is not framed as a final external-validity claim. It
is framed as a methods and evidence paper that identifies exactly what
has been demonstrated and what remains before academic submission.

\begin{table}[h]
\centering
\caption{Readiness against the stated validation gates.}
\label{tab:review-readiness}
\input{tables/review_readiness}
\end{table}

For a technical review team, the principal review questions are now concrete.
First, does Frank's source-to-packet artifact preserve the legally controlling
facts and avoid answer leakage in the generated question? Second, does Karthic's
rubric capture the relevant gates, defenses, counterarguments, source limits,
and variation sensitivity without double-counting? Third, do Dasha's three
observed clusters reflect meaningful legal-reasoning differences or merely
over-split wording differences? Fourth, does the judge apply each rubric row in
a legally defensible way, and are the projected model rankings stable under
judge repeats or alternate judge models? Fifth, are Zak triggers sufficiently
sensitive to low-confidence or mixed-cluster cases?

The answers to those questions determine the next research milestone. The
reported implementation satisfies the pipeline-readiness standard: a source case
can produce all major artifacts and pass most executable internal gates. A
separate method-readiness report now makes the remaining gaps explicit rather
than treating the run as a binary success. The current report marks seven of ten
gates as met, marks run-bundle integrity as met, marks judge reliability as
partial because the saved live run was not repeated or panel-judged, marks
preflight as partial because a credential warning remains, and marks live
perturbation validation as an evidence gap. The
implementation therefore does not yet satisfy the stronger publication-readiness
standard, which requires frozen prompts and settings, held-out source cases,
expert review, target reliability thresholds, qualitative error analysis, and
paper tables generated from frozen review evidence.
