\section{Experimental Design and Validation}

The validation protocol tests whether each automated stage produces a
source-grounded artifact that is usable by the next stage without manual
patching. The protocol is internal: it measures reproducibility, schema
integrity, perturbation behavior, cluster coherence, judge stability, and
artifact quality before external legal-expert review. A generated run bundle is
the unit of analysis. It contains the Frank packet, Karthic rubric, response
artifacts, Dasha clusters, judge scores, Zak packets, manifest, validation
summary, tables, and prompt-provenance records.

The internal validator checks five stage families, and the paper separately
reports a stage-level artifact assessment. Frank passes when the packet
contains a doctrine, source-grounded question, variations, gold answer, and
a complete downstream handoff record. Karthic passes when the rubric has enough rows, canonical
categories, non-duplicated criteria, and source-support snippets. Dasha has two
separate gates. The coverage gate passes when unlabeled model answers to the
same Frank question are all assigned to clusters after response generation, with
no preassigned reasoning labels used as input. The divergence gate passes only
when the configured live run observes at least the required number of distinct
legal-reasoning clusters. Judge passes when every cluster receives every rubric
row score, model rankings are generated, and any repeated-judge stability report
does not require review. Zak passes when escalation packet state is explicitly
captured, including escalation for unstable repeated judge rows when applicable.
Perturbation validation passes when the run contains both invariant and material
question edits, invariant edits preserve the dominant legal answer path, and
material edits change the dominant answer path or reasoning signature. This is a
domain-specific metamorphic test: the validation target is the relation between
the original and edited legal questions, not a standalone answer label for each
question.

The validation logic is implemented as executable checks rather than prose-only
review. Frank checks target packet completeness and deprecated-heading failure
modes. Karthic checks row count, required category coverage, duplicate-like row
criteria, source-support fields, and weight normalization. Dasha checks that all
responses are assigned to clusters, that clusters are internally consistent under
the same normalized signature-bucket function used by the clustering step, and
that each member's normalized signature key agrees with its centroid key. It
also checks that no unexpected non-Latin text appears in legal signals. Judge checks that the
number of returned row scores equals \texttt{clusters} times \texttt{rubric
rows}, that every model receives projected member scores, and that rankings are
materialized. When judge repeats or judge panels are configured, it also checks
the stability summary produced from repeated or panel row scores and records the
panel composition. Zak checks explicit escalation state even when no packet is
needed.
These checks were chosen because they correspond to the pipeline's main failure
modes: unsupported legal framing, generic rubrics, schema drift, paraphrase
over-splitting, missing judge rows, and silent escalation failure.

The statistical layer adds uncertainty estimates to those executable gates. The
implementation reports Wilson intervals for binomial rates such as
member/centroid coherence and unstable judge rows; bootstrap intervals for
cluster sizes, feature similarity, and projected model scores; permutation tests
over categorical answer-family distributions for perturbation tracks; pairwise
mean absolute error and weighted \(\kappa\) for judge-panel agreement; and
macro-F1, purity, and completeness for the controlled 500-response regression.
These statistics are reported as diagnostics of the method under the current
run design. They are not used to claim population-level model superiority from
one case.

The evidence package has five layers. First, unit and regression tests
exercise config loading, prompt hashing, Frank packet completeness, Karthic
rubric coverage, Dasha clustering invariants, judge projection, repeated-judge
and panel-judge stability aggregation, Zak escalation, model-call clients, and
statistical metrics. Second, a real live batch
executes the full LLM-driven path using ten response model identifiers with two
samples per model over three question tracks, yielding 60 natural answers.
Third, a natural-response Dasha audit
checks that the clustered inputs are unlabeled model answers to one Frank
question, not responses generated from preassigned reasoning categories. It also
checks whether the batch produced enough observed reasoning divergence to stress
Dasha and whether each clustered member agrees with its centroid key. Fourth, a
deterministic 500-response regression suite tests the
clustering container on eight known Statute-of-Frauds signatures; that suite is
a scale and bookkeeping check, not the main evidence for Dasha's discovery
behavior. Fifth, a perturbation smoke test executes an original question,
an invariant party-name edit, and a material no-writing edit, then verifies that
the invariant edit preserves the answer path while the material edit changes it.

The validation is intentionally layered. Unit tests isolate parser and invariant
logic without paying for model calls. The natural-response batch then exercises
the live path that matters scientifically: multiple model outputs answer the
same source-derived legal question before Dasha sees them. The reported run
passes the configured Dasha divergence gate because it produced 23
track-aware observed reasoning clusters against a target of two, but it remains
a bounded single-case sample. The deterministic 500-response regression is retained
because it catches implementation regressions in clustering, projection, and
table generation at the target response scale, but it is not used to claim that
Dasha has discovered reasoning families from unlabeled model text. This
distinction is central to the method: discovery is tested only on unlabeled
model answers; labeled fixtures test software bookkeeping. Separate Zak
regressions force low-margin and unstable-judge conditions so that escalation
packet creation is tested as a positive behavior, not only as an empty
no-escalation record.

A Dasha-specific refinement tests a multi-path legal-answer failure mode.
Using the same 60 saved natural responses, Dasha signatures were regenerated
with a schema that separates the controlling path from secondary paths. A naive
cluster key that included every secondary path produced 49 clusters for 60
responses, which was too fragmented for centroid judging. The retained method
therefore stores the full secondary-path audit profile but clusters on Dasha's
primary canonical fields. The tuned track-aware pass
produced 23 clusters across the original, invariant, and material tracks after
repairing a normalization bug around negative enforceability language. Judge was
then rerun on those multi-path clusters, producing 230 final row-level scores,
projected scores for all 60 member responses, and updated model rankings.

The internal review layer then asks the legal-methodological questions that
schema checks cannot answer by themselves: whether Frank's framing is what a
researcher expected from the source and instruction examples; whether Karthic's
rows are legally useful rather than generic; whether Dasha's sampled cluster
members share a legal theory with their centroid; and whether the judge
rationales follow the rubric rows. The manuscript therefore reports
both executable gates and human-readable artifact examples. The executable gates
make the run reproducible; the artifact assessment makes the legal quality
claim inspectable.

This protocol does not replace expert legal review. It is the complete internal
evidence gate before any external claim: the pipeline must prove that it can
run, preserve provenance, expose errors, cluster at controlled scale, and
generate coherent artifacts before any stronger publication claim is made.
